---
title: "Q3_Q10"
author: "Aishwarya Tiwari"
date: "2023-04-27"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tm)
library(wordcloud)
library(dplyr)
setwd("~/Desktop/Course Notes/ACC 882-Project Management/Project/Data")
```

## Define the category

```{r Add_to_basket}
setwd("~/Desktop/Course Notes/ACC 882-Project Management/Project/Data")
shopper=read.csv("export_shopper.txt",header=TRUE,sep="\t")
shopper=shopper%>%arrange(panelistid,eventtimeutc)
catshopper=shopper%>%filter(category %in% c("Sports & Outdoors","Shoes"))
index1=grepl(" exercise ",tolower(shopper$productname))
index2=grepl(" fitness ",tolower(shopper$productname))
index3=grepl(" gym ",tolower(shopper$productname))
index4=grepl(" health ",tolower(shopper$productname))
index5=grepl(" yoga ",tolower(shopper$productname))
index6=grepl(" workout ",tolower(shopper$productname))
index7=grepl(" fitness equipment ",tolower(shopper$productname))
index8=grepl(" nutrition ",tolower(shopper$productname))
catshopper2=shopper[index1|index2|index3|index4|index5|index6|index7|index8,]
index9=grepl(" household",tolower(catshopper2$productname))
catshopper2=catshopper2[!index9,]
catshopper=rbind(catshopper,catshopper2)
catshopper=catshopper[!duplicated(catshopper),]
rm(catshopper2)

catshopper$shopperdate=substring(catshopper$eventtimeutc,first=1,last=10)
catshopper$shoppertime=strptime(catshopper$eventtimeutc,"%Y-%m-%d %H:%M:%S",tz="UTC")
catshopper=catshopper%>%select(-starts_with("eventtime"))

write.table(catshopper,"catshopper.txt",sep="\t",row.names=FALSE,col.names=TRUE)
purchase=catshopper%>%filter(eventtype=="Purchase")%>%
  arrange(panelistid,shoppertime)%>%
  select(panelistid,shoppertime,shopperdate,productname)
write.table(purchase,"purchase.txt",sep="\t",row.names=FALSE,col.names=TRUE)

# We have 1140 purchases with 590 unique panelist ID
users=purchase%>%group_by(panelistid)%>%summarize()
```

## SEO strategies

#### Shopppr Data || Add to basket

```{r Add_to_basket}
#Add to Basket by panelistids who had purchased a product in shopper table
#preprocesssing
data_wc = read.csv("/Users/aishwaryatiwari/Desktop/Course Notes/ACC 882-Project Management/Project/Data/catshopper.txt",header=TRUE,sep="\t")
data_wc = data_wc%>%filter(eventtype=="Add to Basket")
my_corpus=Corpus(VectorSource(data_wc$productname))
my_corpus[[1]][[1]]
getTransformations()
my_corpus = tm_map(my_corpus, content_transformer(tolower))
my_corpus = tm_map(my_corpus,removeWords,stopwords("english"))
my_corpus = tm_map(my_corpus, removeWords, c("amp"))
my_corpus = tm_map(my_corpus, removePunctuation)
my_corpus = tm_map(my_corpus, removeNumbers)
my_corpus = tm_map(my_corpus, stripWhitespace)

#construct the document term matrix
mat=TermDocumentMatrix(my_corpus)
mat=as.matrix(mat)
v = sort(rowSums(mat),decreasing=TRUE)

#Word cloud
par(mar = c(5, 5, 5, 5))
wordcloud(word = names(v),freq = v,max.words = 150,random.order = FALSE, min.freq = 5, color = brewer.pal(8,'Dark2'),scale = c(5,0.3))
```
#### Summary of Shopppr Data || Add to basket

```{r}
#Summary Statistics
df = data.frame(v)
head(df,20)
```

#### Shopppr Data || Purchase

```{r Purchase}
#Add to Basket by panelistids who had purchased a product
#preprocesssing
data_wc = read.csv("/Users/aishwaryatiwari/Desktop/Course Notes/ACC 882-Project Management/Project/Data/catshopper.txt",header=TRUE,sep="\t")
data_wc = data_wc%>%filter(eventtype=="Purchase")
my_corpus=Corpus(VectorSource(data_wc$productname))
my_corpus[[1]][[1]]
getTransformations()
my_corpus = tm_map(my_corpus, content_transformer(tolower))
my_corpus = tm_map(my_corpus,removeWords,stopwords("english"))
my_corpus = tm_map(my_corpus, removeWords, c("amp"))
my_corpus = tm_map(my_corpus, removePunctuation)
my_corpus = tm_map(my_corpus, removeNumbers)
my_corpus = tm_map(my_corpus, stripWhitespace)

#construct the document term matrix
mat=TermDocumentMatrix(my_corpus)
mat=as.matrix(mat)
v = sort(rowSums(mat),decreasing=TRUE)

#Word cloud
par(mar = c(5, 5, 5, 5))
wordcloud(word = names(v),freq = v,max.words = 150,random.order = FALSE, min.freq = 5, color = brewer.pal(8,'Dark2'),scale = c(5,0.3))
```
#### Summary of Shopppr Data || Purchase

```{r}
#Summary Statistics
df = data.frame(v)
head(df,20)
```

#### Web Data

```{r web_table}
#Web search term results by panelistids who had purchased a product in web table
#preprocesssing
data_wc = read.csv("/Users/aishwaryatiwari/Desktop/Course Notes/ACC 882-Project Management/Project/Data/relatedweb.txt",header=TRUE,sep="\t")
my_corpus=Corpus(VectorSource(data_wc$searchterm))
my_corpus[[1]][[1]]
getTransformations()
my_corpus = tm_map(my_corpus, content_transformer(tolower))
my_corpus = tm_map(my_corpus,removeWords,stopwords("english"))
my_corpus = tm_map(my_corpus, removePunctuation)
my_corpus = tm_map(my_corpus, removeNumbers)
my_corpus = tm_map(my_corpus, stripWhitespace)

#construct the document term matrix
mat=TermDocumentMatrix(my_corpus)
mat=as.matrix(mat)
v = sort(rowSums(mat),decreasing=TRUE)

#Word cloud
par(mar = c(5, 5, 5, 5))
wordcloud(word = names(v),freq = v,max.words = 150,random.order = FALSE, min.freq = 5, color = brewer.pal(8,'Dark2'),scale = c(5,0.3))
```
#### Summary of Web Data

```{r}
#Summary Statistics
df = data.frame(v)
head(df,20)
```

#### Purchase journey: Is Social Media driving our users

```{r}
# Social data within 0-6 hours of purchase
relatedsocial=read.csv("/Users/aishwaryatiwari/Desktop/Course Notes/ACC 882-Project Management/Project/Data/relatedsocial.txt",header=TRUE,sep="\t")

advertisers = sqldf('SELECT relatedsocial.advertiser, COUNT(*) AS Number_of_ads
      FROM purchase 
      INNER JOIN relatedsocial ON purchase.panelistid = relatedsocial.panelistid 
      AND purchase.shopperdate = relatedsocial.shopperdate
      GROUP BY relatedsocial.advertiser
      ORDER BY Number_of_ads DESC
      LIMIT 20')
write.table(advertisers,"advertisers.txt",sep="\t",row.names=FALSE,col.names=TRUE)

```

#### Purchase journey of super users

```{r}
setwd("~/Desktop/Course Notes/ACC 882-Project Management/Project/Data")
library(readxl)
library(sqldf)
superusers = read_excel("SuperUsers.xlsx")
catshopper = read.csv("/Users/aishwaryatiwari/Desktop/Course Notes/ACC 882-Project Management/Project/Data/catshopper.txt",header=TRUE,sep="\t")
supershopper = sqldf("SELECT superusers.*,catshopper.eventtype, catshopper.productname, catshopper.category, catshopper.shopperdate,	catshopper.shoppertime,catshopper.searchterms
                     FROM superusers
                     LEFT JOIN catshopper
                     ON superusers.panelistid = catshopper.panelistid
                     ORDER BY superusers.Count DESC")
num_views = supershopper %>% group_by(panelistid,eventtype) %>% summarise(counts = n())
write.table(num_views,"num_views.txt",sep="\t",row.names=FALSE,col.names=TRUE)

my_data = supershopper %>% select(userid = panelistid, event.type = eventtype, product.name=productname, shopper.date = shopperdate, shopper.time = shoppertime)
my_data$datetime = as.POSIXct(paste(my_data$shopper.date, my_data$shopper.time))
unique_combinations = unique(my_data[, c("userid", "event.type", "product.name")])
earliest_datetimes = aggregate(datetime ~ userid + product.name + event.type, data = my_data, FUN = min)
merged_data = merge(unique_combinations, earliest_datetimes, by = c("userid", "product.name", "event.type"))
wide_data = reshape(merged_data, idvar = c("userid", "product.name"), timevar = "event.type", direction = "wide")
colnames(wide_data) = c("userid", "product.name", "first.viewed", "first.added.to.basket", "first.purchased")
write.table(wide_data,"wide_data.txt",sep="\t",row.names=FALSE,col.names=TRUE)

purchased_items <- subset(my_data, event.type == "Purchase")
merged_purchased = merge(purchased_items, wide_data, by = c("userid", "product.name"))
merged_purchased$diff.added.to.basket = difftime(merged_purchased$first.purchased, merged_purchased$first.added.to.basket)
merged_purchased$diff.viewed = difftime(merged_purchased$first.purchased, merged_purchased$first.viewed)
write.table(merged_purchased,"merged_purchased.txt",sep="\t",row.names=FALSE,col.names=TRUE)
```

#### Digital FootPrint: Most common app categories

```{r}
# App data within 0-6 hours of purchase
sqldf('SELECT relatedapp.appcategory, AVG(sessionduration) as timespent
      FROM purchase 
      INNER JOIN relatedapp ON purchase.panelistid = relatedapp.panelistid 
      AND purchase.shopperdate = relatedapp.shopperdate
      GROUP BY relatedapp.appcategory
      ORDER BY timespent DESC
      LIMIT 20')
```

#### Digital FootPrint: Are users searching for product?

```{r}
# Web data within 0-6 hours of purchase
relatedweb=read.csv("/Users/aishwaryatiwari/Desktop/Course Notes/ACC 882-Project Management/Project/Data/relatedweb.txt",header=TRUE,sep="\t")
table_analysis = sqldf('SELECT purchase.productname, relatedweb.searchterm
            FROM purchase
            INNER JOIN relatedweb
            ON purchase.panelistid = relatedweb.panelistid
            AND purchase.shopperdate = relatedweb.shopperdate
            WHERE relatedweb.searchterm != ""
            GROUP BY purchase.productname')
table_analysis$productname = tolower(table_analysis$productname)
table_analysis$productname = str_trim(table_analysis$productname) #remove whitespace from start/end
table_analysis$productname = str_replace_all(table_analysis$productname, "  ", "") #remove double whitespaces
table_analysis$searchterm = str_trim(table_analysis$searchterm) #remove whitespace from start/end
table_analysis$searchterm = str_replace_all(table_analysis$searchterm, "  ", "") #remove double whitespaces
write.table(table_analysis,"table_analysis.txt",sep="\t",row.names=FALSE,col.names=TRUE)
# table_analysis$match <- sapply(table_analysis$product_name, function(x) grepl(gsub(" ", ".*",table_analysis$search_term),x))
```


